---
title: "Initial Data Exploration"
author: "Henry Shiffer"
output: github_document
always_allow_html: true
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```








# Data Exploration:


This data is from Inside Airbnb (www.insideairbnb.com) (Cox, 2021). In this section we will preform some explanatory statistics of Toronto's Airbnb data from the month February 2021.




```{r message = FALSE}
library(sf)
library(mapview)
library(tidyverse) 
library(tidymodels) 
library(visdat) 
library(ggmap)
```


We can load Toronto's February 2021 Airbnb data into R by:

```{r message = FALSE}
feb_21_airbnb <- read_csv("Airbnb February 2021.csv", guess_max = 20000)
```





To get a high level view of the data and it's attributes, we can use the **glimpse()** function from the package **tidyverse**.

```{r}
glimpse(feb_21_airbnb)
```





## Exploring Prices


We can see that the price column contains both dollar signs and commas when the data was scraped. We are going to want to remove the dollar signs and commas and convert these values to integers to be able to graph these values. 

```{r}
glimpse(feb_21_airbnb$price)
```







Now for cleaning the price column by removing all dollar signs and commas and converting these values to integers.


```{r}
feb_21_airbnb <- feb_21_airbnb %>% 
  mutate(price = str_remove(price, "\\$"),
         price = str_remove(price, ","),
         price = as.integer(price)
         )
glimpse(feb_21_airbnb$price)
```




We can plot the Airbnb price per night data on the X-axis with number of properties having that price per night on the Y-axis. It can be observed that the distribution is strongly right skewed. We can examine if this skew still exists zooming in closer at the prices per night.


```{r}
feb_21_airbnb %>%
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 20) +
  theme_classic() +
  labs(x = "February 2021 Price per night",
       y = "February 2021 number of properties")
```





It is clear there are definitely some outliers existing in price per night. We can split the data and look at prices per night greater than $500 and less than $500.  


```{r}
feb_21_airbnb %>%
  filter(price > 500) %>% 
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 10) +
  theme_classic() +
  labs(x = "Price per night greater than 500",
       y = "Number of properties")
```



The right skew still exists when examining price per night greater than 500. As we have a much better view of the outliers, we can see that there exists properties that are greater than $10,000 a night. 



We can can get a better view of these higher end prices by examining the amount of properties greater than $10,000 a night.  


```{r}
feb_21_airbnb %>%
  filter(price > 10000) %>% 
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 10) +
  theme_classic() +
  labs(x = "Price per night greater than 10,000",
       y = "Number of properties")
```




It appears that the highest price in February 2021 is $13,000 a night, and there are 3 properties that have this price.




We can take a look at the property types that are $13,000:




```{r}
price_13000_listings <- subset(feb_21_airbnb, price == 13000)
price_13000_listings <- subset.data.frame(select = c("price",
                                                     "neighbourhood",
                                                     "name",
                                                     "property_type",
                                                     "room_type",
                                                     "host_id",
                                                     "minimum_nights",
                                                     "maximum_nights",
                                                     "bedrooms"),
                                          price_13000_listings)
price_13000_listings
```






We can see that the properties that have the price of $13,000 per night are entire condominiums and bungalows. However, despite the high price of the properties, these prices have 1 to 2 bedrooms.









Now we can look at properties less than $500. 






```{r}
feb_21_airbnb %>%
  filter(price < 500) %>% 
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 1) +
  theme_classic() +
  labs(x = "Price per night less than 500",
       y = "Number of properties")
```



We can see a majority of prices are less than $100 a night.




We can take a further look at these values less than $100. 


```{r}
feb_21_airbnb %>%
  filter(price < 100) %>% 
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 1) +
  theme_classic() +
  labs(x = "Price per night less than 100",
       y = "Number of properties")
```


To get a sense of the trends in the most affordable Airbnbs, we can zoom on the properties that are less than $25 per night.



```{r}
feb_21_airbnb %>%
  filter(price < 25) %>% 
  ggplot(aes(x = price)) +
  geom_histogram(binwidth = 1) +
  theme_classic() +
  labs(x = "Price per night less than 25",
       y = "Number of properties")
```



It can be examined that a majority of properties that are less than $25 per night are around $20 per night. We can also see that there exists some properties that are $0. It is very unlikely that there are actually Airbnb's that are $0.


It makes sense to take a look at these properties that have a price of $0 more closely.



```{r}
price_0_listings <- subset(feb_21_airbnb, price == 0)
price_0_listings <- subset.data.frame(select = c("price", "neighbourhood", "name","property_type", "room_type", "host_id", "minimum_nights", "maximum_nights"), price_0_listings)
price_0_listings
```



Both properties that have a price of $0 per night are hotel rooms in the "Residence & Conference Centre" in Toronto. It also seems that both properties are listed by different hosts as there are different host identification numbers. We can see for both a person can stay for a minimum of 28 nights and for a maximum of 365 nights.

An Airbnb listing for $0 per night is very untrustworthy. These may be data-collection errors, or scams.

However, it is possible that these units in this building may be affordable housing alternatives and a great deal!














## Property Type



We can get a better view of property types and the amount of properties of each type.



```{r}
ggplot(feb_21_airbnb, aes(property_type)) + geom_bar(binwidth = 100, stat = "count") + theme(text = element_text(size=9), axis.text.x = element_text(angle=90, hjust=1))
```



We can see from this visual that entire apartment and entire condominium are the most represented Toronto Airbnb property types for February 2021. 


We can also check which property type has the lowest representation.













## Nights able to stay:



We can also gain a view of the minimum amount of nights available to book a stay at the Airbnb.




```{r}
feb_21_airbnb %>%
  ggplot(aes(x = minimum_nights)) +
  geom_histogram(binwidth = 5) +
  theme_classic() +
  labs(x = "Minimum night booking availability",
       y = "Number of properties")
```




We can zoom in on properties that have a 100 night minimum booking or less.





```{r}
feb_21_airbnb %>%
  filter(minimum_nights < 100) %>% 
  ggplot(aes(x = minimum_nights)) +
  geom_histogram(binwidth = 1) +
  theme_classic() +
  labs(x = "Minimum night booking availability",
       y = "Number of properties")
```

#Compare March 2020 to April 2020 when recieve April 2020 data

We can see that the majority of properties have a minimum amount of night booking of around 28. This makes sense as in April 2020, Ontario had banned all short term rentals (a rental period of less than 28 days) unless the unit is being rented to someone in need of housing during the "Emergency Order". 






## Mapping Prices:


To see how prices in February 2021 compare to the pre-pandemic months of February 2019 and February 2020. We can load this data into R and map these 3 month's prices 


```{r warning = FALSE, message=FALSE}
feb_19_airbnb <- read_csv("Airbnb February 2019.csv", guess_max = 20000)
feb_20_airbnb <- read_csv("Airbnb February 2020.csv", guess_max = 20000)
```



We can now clean the price column of both February 2019 and February 2020, like we did for February 2021.


```{r}
feb_19_airbnb <- feb_19_airbnb %>% 
  mutate(price = str_remove(price, "\\$"),
         price = str_remove(price, ","),
         price = as.integer(price)
         )

feb_20_airbnb <- feb_20_airbnb %>% 
  mutate(price = str_remove(price, "\\$"),
         price = str_remove(price, ","),
         price = as.integer(price)
         )
```




We can plot the prices of February 2019, February 2020, and February 2021 on a map of Toronto. 


```{r}
feb_19_airbnb_sf <- st_as_sf(feb_19_airbnb, coords = c("longitude", "latitude"), crs = 4326)
feb_20_airbnb_sf <- st_as_sf(feb_20_airbnb, coords = c("longitude", "latitude"), crs = 4326)
feb_21_airbnb_sf <- st_as_sf(feb_21_airbnb, coords = c("longitude", "latitude"), crs = 4326)
```



```{r}
mapview(feb_19_airbnb_sf, zcol = "price", legend = TRUE)
```


```{r}
mapview(feb_20_airbnb_sf, zcol = "price", legend = TRUE)
```


```{r}
mapview(feb_21_airbnb_sf, zcol = "price", legend = TRUE)
```





References:

(Rohan Alexander, 2021) Telling Stories With Data https://www.tellingstorieswithdata.com/exploratory-data-analysis.html#case-study---airbnb-listing-in-toronto



