---
title: "More Data Exploration"
author: "Henry Shiffer"
output: github_document
always_allow_html: true
---


# Continued Data Exploration and Initial Modelling:




```{r message = FALSE}
library(tidyverse) 
library(tidymodels) 
library(ggmap)
library(varhandle)
library(caret)
library(readr)
library(yardstick)
```




In this section will continue exploring Toronto's February 2021 Airbnb data and build some initial models.







Loading Toronto's February 2021 Airbnb data into R by:


```{r message = FALSE}
feb_21_airbnb <- read_csv("AirbnbFebruary2021.csv", guess_max = 20000)
glimpse(feb_21_airbnb)

#getting rid of the $ and , in price
feb_21_airbnb <- feb_21_airbnb %>% 
  mutate(price = str_remove(price, "\\$"),
         price = str_remove(price, ","),
         price = as.integer(price)
         )
```




A note: The Airbnb data is being called locally and is not on Github.


## Review Scores Map:


We can gain a view of where in Toronto has the highest and lowest Airbnb review score ratings. To do this the NA values must be filtered out before these values can be mapped.




```{r message=FALSE}
#getting rid of NA values for review_scores_rating in the original data-set
rsr_filtered_airbnb <- feb_21_airbnb %>%
  filter(!is.na(review_scores_rating))

#scale_colour_distiller(palette = "RdYlBu")
#mapping the NA value filtered review_scores_ratings values
rsr_filtered_borders <- c(bottom  = min(rsr_filtered_airbnb$latitude), 
                top = max(rsr_filtered_airbnb$latitude),
                left = min(rsr_filtered_airbnb$longitude),
                right = max(rsr_filtered_airbnb$longitude))
map1 <- get_stamenmap(rsr_filtered_borders, maptype = "toner-lite")
ggmap(map1) + geom_point(data = rsr_filtered_airbnb, mapping = aes(x = longitude, y = latitude, 
                                               col = review_scores_rating)) +
  scale_colour_distiller(palette = "RdYlBu") +
  geom_jitter(alpha = 0.4) + ggtitle("Feb 2021 Review Scores")
```






## Superhosts Map:

A map of superhosts would also be interesting. From the Airbnb website (https://www.airbnb.ca/help/article/829/how-do-i-become-a-superhost), a superhost is defined as a host who has met all of the following requirements:


> "Completed at least 10 trips OR completed 3 reservations that total at least 100 nights"

> "Maintained a 90% response rate or higher"

> "Maintained a 1% percent cancellation rate (1 cancellation per 100 reservations)"

> "Maintained a 4.8 overall rating (this rating looks at the past 365 days of reviews, based on the date the guest left a review, not the date the guest checked out)"



If these listings have hosts that are superhosts, the listings have a better chance of being better maintained and of higher quality to stay in. 



```{r message=FALSE}
#getting rid of NA values for host_is_superhost in the original data-set
super_filtered_airbnb <- feb_21_airbnb %>%
  filter(!is.na(host_is_superhost))

#mapping the NA value filtered host_is_superhost values
super_filtered_borders <- c(bottom  = min(super_filtered_airbnb$latitude), 
                top = max(super_filtered_airbnb$latitude),
                left = min(super_filtered_airbnb$longitude),
                right = max(super_filtered_airbnb$longitude))
map2 <- get_stamenmap(super_filtered_borders, maptype = "toner-lite")
ggmap(map2) + geom_point(data = super_filtered_airbnb, mapping = aes(x = longitude, y = latitude, 
                                               col = host_is_superhost)) + 
  geom_jitter(alpha = 0.4) + ggtitle("Feb 2021 Superhosts")
```



We can see that there does exists a good amount of superhost listings, but ultimately it looks like there is more hosts that do not have superhost status.





## Bedrooms Map:



To also get a sense of listing quality, we can plot bedroom amount on the map.


```{r message=FALSE}
#getting rid of NA values for host_is_superhost in the original data-set
bedrooms_filtered_airbnb <- feb_21_airbnb %>%
  filter(!is.na(bedrooms))

#mapping the NA value filtered host_is_superhost values
bedrooms_filtered_borders <- c(bottom  = min(bedrooms_filtered_airbnb$latitude), 
                top = max(bedrooms_filtered_airbnb$latitude),
                left = min(bedrooms_filtered_airbnb$longitude),
                right = max(bedrooms_filtered_airbnb$longitude))
map3 <- get_stamenmap(bedrooms_filtered_borders, maptype = "toner-lite")
ggmap(map3) + geom_point(data = bedrooms_filtered_airbnb, mapping = aes(x = longitude, y = latitude, 
                                               col = bedrooms)) +
  scale_colour_distiller(palette = "RdYlBu") +
  geom_jitter(alpha = 0.4) +
  ggtitle("Feb 2021 Bedroom Amount")
```



We can see an overwhelming amount of listings have less than ~5 bedrooms. This makes sense. Bedroom space is very hard to come by in the city, and these listings reflect that.




## Cleanliness Map:


Regardless of the pandemic, cleanliness is a good indicator of Airbnb listing quality. If a listing has received low review scores for cleanliness, it is unlikely anyone will feel comfortable living in that property. 


We can gain a view of Toronto Airbnb listing cleanliness on a map of the city.



```{r message=FALSE}
#getting rid of NA values for review_scores_cleanliness in the original data-set
clean_filtered_airbnb <- feb_21_airbnb %>%
  filter(!is.na(review_scores_cleanliness))

#mapping the NA value filtered out review_scores_cleanliness values
clean_filtered_borders <- c(bottom  = min(clean_filtered_airbnb$latitude), 
                top = max(clean_filtered_airbnb$latitude),
                left = min(clean_filtered_airbnb$longitude),
                right = max(clean_filtered_airbnb$longitude))
map4 <- get_stamenmap(clean_filtered_borders, maptype = "toner-lite")
ggmap(map4) + geom_point(data = clean_filtered_airbnb, mapping = aes(x = longitude, y = latitude, 
                                               col = review_scores_cleanliness)) +
  scale_colour_distiller(palette = "RdYlBu") +
  geom_jitter(alpha = 0.4) +
  ggtitle("Feb 2021 Cleanliness Ratings")
```



We can see there is definitely many listings that have review scores for cleanliness that are 6 and below. These listings are likely not very well maintained and are possibly used just as a short-term rental property without a host living there.


I would not recommend any listings that are below a cleanliness rating of 6 to anyone, especially during a pandemic.







## Initial Linear Modelling of Feburary 2021 Airbnb data:



We can start fitting simple linear models with the variables we are interested in. 




### Cleaning variables before modelling:


We can see that bathroom amount is categorized as a string. For analysis of bathroom amount, it would make sense to extract the numeric value in the string. 


```{r}
glimpse(feb_21_airbnb$bathrooms_text)
```





```{r warning=FALSE, message=FALSE}
#parse_number() drops any non-numeric characters
feb_21_airbnb$bathrooms_numeric <- parse_number(feb_21_airbnb$bathrooms_text)
```






We must also make sure that price is an integer and not a character. 

```{r}
#stripping away $ and , from price
feb_21_airbnb <- feb_21_airbnb %>% 
  mutate(price = str_remove(price, "\\$"),
         price = str_remove(price, ","),
         price = as.integer(price)
         )

#removing NAs from price
feb_21_airbnb <- feb_21_airbnb %>%
  filter(!is.na(price))
```



We can see that host response rates are coded as characters. We can code them as integers instead.

```{r}
glimpse(feb_21_airbnb$host_response_rate)
```


```{r message = FALSE}
#stripping away % and from host_response_rate and converting to integer
feb_21_airbnb <- feb_21_airbnb %>% 
  mutate(host_response_rate = str_remove(host_response_rate, "\\%"),
         host_response_rate = as.integer(host_response_rate)
         )
```




### Test set and train set:



We can now split the data into a test set and training set to test the accuracy of our model in prediction later on.

```{r}
set.seed(496)

#splitting the data
feb_21_airbnb_split <- 
  feb_21_airbnb %>%
  initial_split(prop = 3/4)

#creating the test and train set
feb_21_airbnb_train <- training(feb_21_airbnb_split)
feb_21_airbnb_test <- testing(feb_21_airbnb_split)

```


### Modelling price with bedrooms:


```{r}
#removing NAs from bedrooms
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(bedrooms))

#price ~ bedrooms model
price_and_bedrooms <- lm(price ~ bedrooms, data = feb_21_airbnb_train)
summary(price_and_bedrooms)
```


We can see that the p-value for the bedrooms covariate is < 2e-16 when that variable is the only predictor.



### Modelling price with bathrooms:




```{r}
#removing any possible NAs still in bathrooms_numeric 
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(bathrooms_numeric))

#price ~ bathrooms model
price_and_bathrooms <- lm(price ~ bathrooms_numeric, data = feb_21_airbnb_train)
summary(price_and_bathrooms)
```


We can see that the p-value for the bathrooms covariate is < 2e-16 when that variable is the only predictor.





### Modelling price with neighbourhood:



```{r}
#removing any possible NAs in neighbourhood_cleansed
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(neighbourhood_cleansed))

#price ~ neighbourhood model
price_and_neighbourhood <- lm(price ~ neighbourhood_cleansed, data = feb_21_airbnb_train)
summary(price_and_neighbourhood)
```



We can see that all the neighbourhood levels within the neighbourhood_cleansed covariate have p-values that are greater than 0.05, which indicates none of these levels are significant in predicting price when neighbourhood_cleansed is the only predictor included in the linear model.














### Modelling Price with cleanliness score:


```{r}
#removing any possible NAs still in review_scores_cleanliness 
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(review_scores_cleanliness))

#price ~ cleanliness model
price_and_cleanliness <- lm(price ~ review_scores_cleanliness, data = feb_21_airbnb_train)
summary(price_and_cleanliness)
```



We can see that the p-value for the cleanliness score covariate is 0.07707 when that variable is the only predictor.




### Modelling Price with overall review score


```{r}
#removing any possible NAs in review_scores_rating 
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(review_scores_rating))

#price ~ overall review score  model
price_and_reviewscore <- lm(price ~ review_scores_rating, data = feb_21_airbnb_train)
summary(price_and_reviewscore)
```





We can see that the p-value for the overall review score covariate is 0.29881 when that variable is the only predictor.
















### Modelling price with reviews per month:



```{r}
#removing any possible NAs in reviews_per_month 
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(reviews_per_month))

#price ~ reviews per month model
price_and_reviewspmonth <- lm(price ~ reviews_per_month, data = feb_21_airbnb_train)
summary(price_and_reviewspmonth)
```



We can see that the p-value for the reviews_per_month covariate is 0.219 when that variable is the only predictor.



### Modelling price with host response rate:



```{r}
#removing any possible NAs in host_response_rate 
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(host_response_rate))

#price ~ host response rate model
price_and_hostresp<- lm(price ~ host_response_rate, data = feb_21_airbnb_train)
summary(price_and_hostresp)
```



We can see that the p-value for the host_response_rate covariate is 0.137 when that variable is the only predictor.





### Modelling price with minimum nights available to book:




```{r}
#removing any possible NAs in minimum_nights
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(minimum_nights))

#price ~ minimum nights model
price_and_minnights <- lm(price ~ minimum_nights, data = feb_21_airbnb_train)
summary(price_and_minnights)
```



We can see that the p-value for the minimum_nights covariate is 1.65e-06 when that variable is the only predictor.






### Modelling price with maximum nights available to book:



```{r}
#removing any possible NAs in maximum_nights
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(maximum_nights))

#price ~ maximum nights model
price_and_maxnights <- lm(price ~ maximum_nights, data = feb_21_airbnb_train)
summary(price_and_maxnights)
```




We can see that the p-value for the maximum_nights covariate is 0.645 when that variable is the only predictor.







### Modelling price with total amount of host listings for a given host:



```{r}
#removing any possible NAs in host_total_listings_count
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(host_total_listings_count))

#price ~ amount of host listings model
price_and_totallists <- lm(price ~ host_total_listings_count, data = feb_21_airbnb_train)
summary(price_and_totallists)
```





We can see that the p-value for the host_total_listings_count covariate is 0.402 when that variable is the only predictor.








### Modelling price with if a host is a Superhost or not:




We can see that the variable host_is_superhost is a logical variable. This indicates it has levels TRUE and FALSE.

```{r}
#viewing type of variable for the host_is_superhost variable
typeof(feb_21_airbnb_train$host_is_superhost)
```




```{r}
#removing any possible NAs in host_is_superhost
feb_21_airbnb_train <- feb_21_airbnb_train %>%
  filter(!is.na(host_is_superhost))

#price ~ is a superhost model without an intercept
price_and_superhost <- lm(price ~ 0 + host_is_superhost, data = feb_21_airbnb_train)
summary(price_and_superhost)


#price ~ is a superhost model with an intercept
price_and_superhost <- lm(price ~ host_is_superhost, data = feb_21_airbnb_train)
summary(price_and_superhost)
```




We can see that when no intercept is included in the model, that both levels of host_is_superhost are significant at the 0.05 significance level. However, when an intercept is included in the model, host_is_superhostTRUE is not significant.




### Modelling price with the selected possibly relevant variables:




Using AIC:


```{r}
#fitting an initial model with all the possibly relevant variables
initial_full_model <- lm(price ~ bedrooms + 
                        bathrooms_numeric + 
                        neighbourhood_cleansed +
                        review_scores_cleanliness +
                        review_scores_rating +
                        reviews_per_month +
                        host_response_rate +
                        minimum_nights +
                        maximum_nights +
                        host_is_superhost,
                        data = feb_21_airbnb_train)
summary(initial_full_model)

stats::step(initial_full_model, direction = "backward")

```






We can see from the AIC backwards selection that the resulting linear model has variables:


> bedrooms 

> bathrooms_numeric

> minimum_nights

> neighbourhood_cleansed

> review_scores_cleanliness

> reviews_per_month

> host_response_rate








### Prediction of Price:


We can now see how the resulting model preforms in prediction.



```{r}
#initial price model
price_inital_model <- lm(formula = price ~ bedrooms + bathrooms_numeric + neighbourhood_cleansed + 
    review_scores_cleanliness + reviews_per_month + host_response_rate, 
    data = feb_21_airbnb_train)
  

#summary of the initial price model
summary(price_inital_model)
#making price predictions
price_predictions <- c(predict(price_inital_model, feb_21_airbnb_test))
#true values of price
price_feb <- c(feb_21_airbnb_test$price)
#computing RMSE with the yardstick package
yardstick::rmse_vec(price_feb, price_predictions)
```






We can see that both the RMSE is high (333.8244), and the R-squared for the model is low (0.2492). This indicates that this linear regression model preformed poorly in predicting price in February 2021.













